MS_CNuptake.Rmd

### 2022-10-23 MS_CNuptake.Rmd
tiny update and fig.4's code all checked

@@

```{r}
#fig.2 validation
plot_grid(p1,p2,p5,
          p8,p9,p10,
          p3,p4,p11,
          p6,p12,p7, 
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)','(j)','(k)','(l)'),
          ncol=3,label_x = 0.9,label_y=0.92,label_size = 25)+white
ggsave(paste("./output/fig1.jpg",sep=""),width = 24, height = 25)

@@

#produce forest NUE vs. forest BP-leaf/BP
nue_f_output <- npp_f/nuptake_f
lnpp_allocation_f_output <- lnpp_f/anpp_f
data_output <- as.data.frame(cbind(nue_f_output,lnpp_allocation_f_output))
ggplot(data=data_output, aes(x=lnpp_allocation_f_output, y=nue_f_output))+
  geom_point()+
  geom_smooth(method="lm")+xlab("Leaf-BP/ABP")+ylab("NUE")+
  theme(axis.text=element_text(size=10),axis.title=element_text(size=15))
ggsave(paste("./output/figs8.jpg",sep=""),width = 5, height = 5)

@@

plot_grid(a3,a4,a5,a6,
          a7,a8,a9,a10,
          a11,a12,a13,a14,
          nrow=3,
          rel_widths = c(4.5/12, 1.5/12,4.5/12,1.5/12),
          labels = c('(a)',' ','(b)',' ',
                     '(c)',' ','(d)',' ',
                     '(e)',' ','(f)',' '))
ggsave(paste("./output/fig2.jpg",sep=""),width = 16, height = 12)

@@

plot_grid(a1,a2,a3,a4,a5,a6,a7,a8,a9,
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
ggsave(paste("./output/fig3.jpg",sep=""),width = 22, height = 10)

plot_grid(aa1,aa2,aa3,aa4,aa5,aa6,aa7,aa8,
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
ggsave(paste("./output/figs7.jpg",sep=""),width = 22, height = 10)
```

@@

sitemean3_final$ORCHICNP_fNup[sitemean3_final$ORCHICNP_fNup==0] <- NA
sitemean3_final$ISAM_npp[sitemean3_final$ISAM_npp==0] <- NA
sitemean3_final$LPX_NPP[sitemean3_final$LPX_NPP==0] <- NA
sitemean3_final$LPX_fNup[sitemean3_final$LPX_fNup==0] <- NA

@@

ggsave(paste("./output/figs8.jpg",sep=""), width = 20, height = 10)

@@

ggsave(paste("./output/figs6.jpg",sep=""), width = 20, height = 10)
```

>>>>

(the partial relationship figure Fig.1 was in ~/yunkepeng/nimpl_sofun_inputs_final/submission_newphytol/submission/plot_all_models.R since here cannot output figures due to too large margins)

@@

```{r}
#fig.2 validation
plot_grid(p1,p2,p5,
          p8,p9,p10,
          p3,p4,p11,
          p6,p12,p7, 
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)','(j)','(k)','(l)'),
          ncol=3,label_x = 0.9,label_y=0.92,label_size = 25)+white
ggsave(paste("./output/fig2.jpg",sep=""),width = 24, height = 25)

@@

#produce forest NUE vs. forest BP-leaf/BP
nue_f_output <- npp_f/nuptake_f
lnpp_allocation_f_output <- lnpp_f/anpp_f
data_output <- as.data.frame(cbind(nue_f_output,lnpp_allocation_f_output))
ggplot(data=data_output, aes(x=lnpp_allocation_f_output, y=nue_f_output))+
  geom_point()+
  geom_smooth(method="lm")+xlab("Leaf-BP/ABP")+ylab("NUE")+
  theme(axis.text=element_text(size=10),axis.title=element_text(size=15))
ggsave(paste("./output/figs6.jpg",sep=""),width = 5, height = 5)

@@

plot_grid(a3,a4,a5,a6,
          a7,a8,a9,a10,
          a11,a12,a13,a14,
          nrow=3,
          rel_widths = c(4.5/12, 1.5/12,4.5/12,1.5/12),
          labels = c('(a)',' ','(b)',' ',
                     '(c)',' ','(d)',' ',
                     '(e)',' ','(f)',' '))
ggsave(paste("./output/fig3.jpg",sep=""),width = 16, height = 12)

@@

plot_grid(a1,a2,a3,a4,a5,a6,a7,a8,a9,
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
ggsave(paste("./output/fig3_notused.jpg",sep=""),width = 22, height = 10)

plot_grid(aa1,aa2,aa3,aa4,aa5,aa6,aa7,aa8,
          labels = c('(a)','(b)','(c)','(d)','(e)','(f)','(g)','(h)','(i)'),label_size = 15)+white
ggsave(paste("./output/figs6_notused.jpg",sep=""),width = 22, height = 10)
```

@@

sitemean3_final$ORCHICNP_fNup[sitemean3_final$ORCHICNP_fNup==0] <- NA
sitemean3_final$ISAM_npp[sitemean3_final$ISAM_npp==0] <- NA
sitemean3_final$ISAM_fNup[sitemean3_final$ISAM_fNup==0] <- NA
sitemean3_final$LPX_NPP[sitemean3_final$LPX_NPP==0] <- NA
sitemean3_final$LPX_fNup[sitemean3_final$LPX_fNup==0] <- NA

@@

ggsave(paste("./output/figs7_notused.jpg",sep=""), width = 20, height = 10)

@@

ggsave(paste("./output/figs5.jpg",sep=""), width = 20, height = 10)
```
